\section{Background}

\subsection{Autopilot Software/Hardware}

The most prominent, open source drone autopilot software packages are ArduPilot~\cite{ardupilot_website} and PX4~\cite{pixhawk_website},
which can integrate easily with many additional/custom software packages.
DJI drones, while the most commonly used consumer-grade drones, use proprietary, closed source autopilot software
that has a limited API for interacting with external software.
Thus, ArduPilot and PX4 and custom drones are typically used for research on drones themselves,
while DJI software and drones are typically used for consumer/commercial tasks.
ArduPilot and PX4 communicate using the same open source, customizable protocol - MAVLink~\cite{mavlink_io} -
which has APIs in many different programming languages as well as with \gls{ROS}.

\subsection{Robotics Software}

\gls{ROS} is a common framework for robotics software that faciliates communication, interactivity, and compatibility
between cooperating software modules.
It uses a Publisher/Subscriber model of message passing to allow concurrent programs to communicate,
and even provides infrastructure for communication between threads running on different hardware platforms.
Within the ROS universe are open-source, ready-built tools that are fundamental to common robotics tasks,
such as interfaces to many different sensors and cameras,
modules for rectification, compression, and transmission of images and point clouds,
PID controllers,
coordinate system tranforms,
and much more.
ROS provides a structured means of generating modular solutions to complex robotics problems.

\subsection{Simulation Software}

Simulation allows robotics developers to test algorithms quickly without logistical concerns such as
weather, transportation, damage to hardware, etc.
Gazebo is one of the most common robotics simulators and provides a physics engine,
many simulated worlds and models of items/vehicles,
integration with many robotics tools,
and~-~importantly~-~lots of user-generated content, software plugins, and information.
It has integration with ROS, so that simulated sensors and actuators can provide data and take commands
from ROS modules.
This allows developers to analyze the behavior of their robots during development cheaply and quickly.
Additionally, Gazebo has integration with both PX4 and ArduPilot which, combined with existing (and free)
drone models, can be used to simulate autonomous drone control algorithms in depth.
AirSim is another robotics simulator, but it focuses on providing accurate physics and graphics
and is therefore a heavier software package.
It also has integration with ArduPilot and PX4, so that 

\subsection{Fiducial Markers}

